Red, Blue, or Purple? 2024’s Battleground States Tell a Story

### 2024-11-04 paper/paper.qmd
paper final draft

```{r}
#| label: fig-candidate_fixed
#| fig-cap: "Candidate Fixed Effects in Hierachical Bayesian Model" 
#| echo: false
#| warning: false
#| message: false

>>>>

```{r}

#| label: fig-candidate_fixed
#| fig-cap: "Candidate Fixed Effects in Hierachical Bayesian Model" 
#| echo: false
#| warning: false
#| message: false
